---
title: "R Notebook"
output: html_notebook
---

### Arianna Lupi, Andrea Gonzalez, Nicholas Rivera

# Libraries

```{r}
library(tidyverse)
library(lubridate)
```

# Combining the Data

Various columns within the files have extra columns that are of no interest. We want to bind the data sets together using the rbind() function. In order to do this without errors, we must have matching columns for the data we read into

```{r}
cols_interest <- c("updated_at", "id", "start_date", "end_date", "election_type", 
                   "result_type", "special", "office", "district", "name_raw", 
                   "last_name", "first_name", "suffix", "middle_name", "party", 
                   "jurisdiction", "division", "votes", "votes_type", "total_votes", 
                   "winner", "write_in", "year")
```


We begin by reading in the data.

```{r}
f_path_01 <- "data/20100126__fl__primary__county__raw.csv"
tbl_20100126_fl_primary_county <- read_csv(f_path_01)

f_path_02 <- "data/20100202__fl__primary__county__raw.csv"
tbl_20100202_fl_primary_county <- read_csv(f_path_02)

f_path_03 <- "data/20100223__fl__general__county__raw.csv"
tbl_20100223_fl_general_county <- read_csv(f_path_03)

f_path_04 <- "data/20100323__fl__primary__county__raw.csv"
tbl_20100323_fl_primary_county <- read_csv(f_path_04)

f_path_05 <- "data/20100413__fl__general__county__raw.csv"
tbl_20100413_fl_general_county <- read_csv(f_path_05)

f_path_06 <- "data/20100824__fl__primary__county__raw.csv"
tbl_20100824_fl_primary_county <- read_csv(f_path_06)

f_path_07 <- "data/20101102__fl__general__county__raw.csv"
tbl_20101102_fl_general_county <- read_csv(f_path_07)

f_path_08 <- "data/20110208__fl__primary__county__raw.csv"
tbl_20110208_fl_primary_county <- read_csv(f_path_08)

f_path_09 <- "data/20110301__fl__general__county__raw.csv"
tbl_20110301_fl_general_county <- read_csv(f_path_09)

f_path_10 <- "data/20110628__fl__general__county__raw.csv"
tbl_20110628_fl_general_county <- read_csv(f_path_10)

f_path_11 <- "data/20110920__fl__primary__county__raw.csv"
tbl_20110920_fl_primary_county <- read_csv(f_path_11)

f_path_12 <- "data/20120131__fl__primary__congressional_district_by_county__raw.csv"
tbl_20120131_fl_primary_congress <- read_csv(f_path_12)

f_path_13 <- "data/20120814__fl__primary__county__raw.csv"
tbl_20120814_fl_primary_county <- read_csv(f_path_13)

f_path_14 <- "data/20121106__fl__general__county__raw.csv"
tbl_20121106_fl_general_county <- read_csv(f_path_14)

f_path_15 <- "data/20140826__fl__primary__county__raw.csv"
tbl_20140826_fl_primary_county <- read_csv(f_path_15) %>% # Contains
    select(cols_interest)

f_path_16 <- "data/20140826__fl__primary__precinct__raw.csv"
tbl_20140826_fl_primary_precinct <- read_csv(f_path_16) %>% 
  select(1:23)

f_path_17 <- "data/20141104__fl__general__county__raw.csv"
tbl_20141104_fl_general_county <- read_csv(f_path_17) %>% 
  select(cols_interest)

f_path_18 <- "data/20160315__fl__primary__county__raw.csv"
tbl_20160315_fl_primary_county <- read_csv(f_path_18) %>% 
  select(cols_interest)

f_path_19 <- "data/20160315__fl__primary__precinct__raw.csv"
tbl_20160315_fl_primary_precinct <- read_csv(f_path_19) %>% 
  select(cols_interest)

f_path_20 <- "data/20160830__fl__primary__county__raw.csv"
tbl_20160830_fl_primary_county <- read_csv(f_path_20) %>% 
  select(cols_interest)

f_path_21 <- "data/20160830__fl__primary__precinct__raw.csv"
tbl_20160830_fl_primary_precinct <- read_csv(f_path_21) %>% 
  select(cols_interest)

f_path_22 <- "data/20161108__fl__general__precinct__raw.csv"
tbl_20161108_fl_general_precinct <- read_csv(f_path_22) %>% 
  select(cols_interest)

f_path_23 <- "data/20180828__fl__primary__precinct__raw.csv"
tbl_20180828_fl_primary_precinct <- read_csv(f_path_23) %>% 
  select(cols_interest)

f_path_24 <- "data/20181106__fl__general__precinct__raw.csv"
tbl_20181106_fl_general_precinct <- read_csv(f_path_24) %>% 
  select(cols_interest)

f_path_25 <- "data/20141104__fl__general__precinct__raw.csv"
tbl_20141104_fl_general_precinct <- read_csv(f_path_25, 
                                             col_types = cols(
                                               jurisdiction = col_character()
                                             )) %>% select(cols_interest)

f_path_26 <- "data/20120814__fl__primary__precinct__raw.csv"
tbl_20120814_fl_primary_precinct <- read_csv(f_path_26, 
                                             col_types = cols(
                                               jurisdiction = col_character()
                                             )) %>% select(cols_interest)

f_path_27 <- "data/20121106__fl__general__precinct__raw.csv"
tbl_20121106_fl_general_precinct <- read_csv(f_path_27, 
                                             col_types = cols(
                                               jurisdiction = col_character()
                                             )) %>% select(cols_interest)

f_path_28 <- "data/20161108__fl__general__county__raw.csv"
tbl_20161108_fl_general_county <- read_csv(f_path_28, # Contains Errors, Must address
                                           col_types =  cols(
                                             district = col_character()
                                           )) %>% select(cols_interest)
```

## Binding the rows into one dataset

```{r}
florida_election_data <- rbind(tbl_20100126_fl_primary_county, tbl_20100202_fl_primary_county, 
              tbl_20100223_fl_general_county, tbl_20100323_fl_primary_county, 
              tbl_20100323_fl_primary_county, tbl_20100413_fl_general_county, 
              tbl_20100413_fl_general_county, tbl_20100824_fl_primary_county, 
              tbl_20101102_fl_general_county, tbl_20110208_fl_primary_county, 
              tbl_20110301_fl_general_county, tbl_20110628_fl_general_county, 
              tbl_20110920_fl_primary_county, tbl_20120131_fl_primary_congress, 
              tbl_20120814_fl_primary_county, tbl_20121106_fl_general_county, 
              tbl_20140826_fl_primary_county, tbl_20140826_fl_primary_precinct, 
              tbl_20141104_fl_general_county, tbl_20160315_fl_primary_county, 
              tbl_20160315_fl_primary_precinct, tbl_20160830_fl_primary_county, 
              tbl_20160830_fl_primary_precinct, tbl_20161108_fl_general_precinct, 
              tbl_20180828_fl_primary_precinct, tbl_20181106_fl_general_precinct, 
              tbl_20141104_fl_general_precinct, tbl_20120814_fl_primary_precinct, 
              tbl_20121106_fl_general_precinct, tbl_20161108_fl_general_county)

str(florida_election_data)

# write.csv(Combined_data, "data/project_dataset.csv")
# closeAllConnections()
```

```{r}
fl_elect <- florida_election_data %>% 
  unite(
    candidate, c("first_name", "middle_name", "last_name"),
    sep = " ", 
    na.rm = TRUE
  )
```


# Tidy Data

```{r}

# Replacements Variable

reps <- c("AIP" = "Independent Party", 
  "INT" = "Independent Party", 
  "Constitution Party of Florida"	= "Constitution Party",
  "CPF"	= "Constitution Party",
  "Democrat" = "Democratic Party", 
  "DEM" = "Democratic Party", 
  "GRE" = "Green Party", 
  "Libertarian Party of Florida" = "Libertarian Party", 
  "Libertarian" = "LBT", 
  "LBT" = "Libertarian Party", 
  "LPF" = "Libertarian Party", 
  "NPA" = "No Party Affiliation", 
  "NP" = "No Party Affiliation", 
  "Objectivist Party of Florida" = "Objectivist Party",
  "JPF" = "Objectivist Party", 
  "OBJ" = "Objectivist Party",
  "Justice Party of Florida" = "Justice Party", 
  "Party for Socialism and Liberation - Florida" = "Party for Socialism and Liberation",
  "Peace and Freedom Party of Florida" = "Peace and Freedom Party",
  "PFP" = "Peace and Freedom Party",
  "PSL" = "Justice Party",
  "Reform Party of Florida" = "Reform Party",
  "REF" = "Reform Party",
  "Republican" = "Republican Party",
  "REP" = "Republican Party",
  "Socialist Party of Florida" = "Socialist Party",
  "SOC" = "Socialist Party",
  "The Independence Party of Florida" = "Independence Party"
)

# Use mutate() and str_replace_all()

fl_elect <- fl_elect %>% 
  mutate(
    party = str_replace_all(party, reps) # We want to change the string within the party column
  ) 

# Replacing the NA values in the party column

fl_elect <- fl_elect %>% 
  mutate(
    party = replace_na(party, "No Party Affiliation")
  )

fl_elect <- fl_elect %>% 
  mutate(
    year = year(start_date), 
    month = month(start_date), 
    day = day(start_date)
  ) %>% 
  select(year, month, day, start_date, election_type, office, district, candidate, party, votes)
```


```{r}
parties <- c("Democratic Party", "Republican Party")

fl_elect %>% 
  filter(election_type == "general" & party %in% parties) %>%
  # filter(election_type == "general") %>% 
  select(start_date, party, votes) %>% 
  arrange(desc(start_date)) %>% 
  group_by(start_date, party) %>% 
  summarise(
    VoteCount = sum(votes)
  ) %>% 
  ggplot(mapping = aes(x = factor(start_date), y = VoteCount, fill = party)) +
  geom_col(position = position_dodge()) + 
  coord_flip()
```



```{r}
fl_elect %>% 
  filter(election_type == "general" & year == 2018) %>% 
  group_by(year, party) %>% 
  summarise(
    Votes = n()
  ) %>% 
  ggplot(mapping = aes(y = reorder(party, Votes), x = Votes)) + 
  geom_col(mapping = aes(fill = party))
```

```{r}
fl_elect %>% 
  filter(election_type == "general" & year == 2016) %>% 
  group_by(year, party) %>% 
  summarise(
    Votes = n()
  ) %>% 
  ggplot(mapping = aes(x = Votes, y = reorder(party, Votes))) + 
  geom_col(mapping = aes(fill = party))
```



```{r}
fl_elect %>% 
  filter(str_detect(string = office, pattern = "President|president") & 
           election_type == "general" & 
           candidate != "") %>% 
  group_by(year, candidate) %>% 
  summarise(
    VoteCounts = sum(votes)
  ) %>% 
  ggplot(mapping = aes(x = year, y = log(VoteCounts), color = candidate)) + 
  geom_line() + 
  geom_point()
```


# Base Data

```{r}
base_data <- florida_election_data %>% 
  unite(
    candidate, c("first_name", "middle_name", "last_name"),
    sep = " ", 
    na.rm = TRUE
  )

base_data <- base_data %>% 
  mutate(
    party = str_replace_all(party, reps) # We want to change the string within the party column
  ) 

# Replacing the NA values in the party column

base_data <- base_data %>% 
  mutate(
    party = replace_na(party, "No Party Affiliation")
  )

base_data <- base_data %>% 
  mutate(
    year = year(start_date), 
    month = month(start_date),
    month_abb = month(start_date, label = TRUE),
    day = day(start_date)
  ) %>% 
  select(year, month_abb, month, day, election_type, office, district, jurisdiction, candidate, party, votes)
```



```{r}
base_data %>% 
  
  # Selecting the columns required
  select(year, election_type, votes) %>% 
  
  # Grouping the Data
  group_by(election_type, year) %>% 
  
  # Summarizing the Election votes
  summarise(
    Votes = sum(votes)
  ) %>% 
  ggplot(mapping = aes(x = year, y = Votes, color = election_type)) + 
  geom_line() + 
  geom_point()
```


```{r}
base_data %>% 
  
  # Selecting the columns required
  select(year, month, month_abb, election_type, votes) %>% 
  
  
  # filter(election_type == "primary" & month_abb == "Aug") %>% 
  # filter(election_type == "primary") %>%
  
  
  # Grouping the Data
  group_by(year, month_abb, election_type) %>%
  
  # Summarizing the Election votes
  summarise(
    Votes = sum(votes)
  ) %>% 
  
  complete(year, month_abb) %>% 
  
  fill(Votes, .direction = "downup") %>% 

  ggplot(mapping = aes(x = year, y = Votes, color = election_type)) + 
  geom_point()
```



# Proportion of Vote 2010

```{r}
proportion_vote <- base_data %>% 
  
  # Selecting the columns required
  select(year, district, jurisdiction, election_type, party, votes) %>% 
  
  filter(election_type == "general" & party %in% c("Democratic Party", "Republican Party") & year != 2011) %>% 
  
  group_by(year, party) %>% 
  
  summarise(
    TotalVotes = sum(votes)
  ) %>% 
  pivot_wider(names_from = party, values_from = TotalVotes)

proportion_vote <- proportion_vote %>% 
  rename(
    DEM = 'Democratic Party', 
    REP = 'Republican Party'
  ) %>% 
  mutate(
    Total = DEM + REP
  )

# 2010: Is the proportion significant for Democrats?
x_2010 <- 13740922
n_2010 <- 34143411
prop.test(x = x_2010, n = n_2010, p = NULL, alternative = "two.sided", correct = FALSE)
```



